---
title: "Challenge 1: Mastering RStudio, Git, and Github"
date: "August 31, 2018"
subtitle: 'Due at 6pm on September 14, 2018'
output:
  md_document:
    variant: markdown_github
#    toc: true
  html_document:
    toc: true
#    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this challenge is to get you more comfortable with RStudio, git, Github, and submitting assignments through Github.  You will need to:

1. [Initialize a new project in RStudio.](#initialize-a-new-project)

2. [Part 1: Modifiying an Existing R Notebook](#modifiying-an-existing-r-notebook)
  2. [Make changes to the R Notebook.](#modify-rmarkdown)
  3. [Generate an HTML report](#knit-the-rmarkdown)
  4. [Commit your work](#commit-changes)

3. [Part 2: Make a new R Notebook](#new-r-notebook)
    1. [Knit the Rmarkdown file to generate an HTML report](#knit-the-rmarkdown)
    2. [Commit your work](#commit-changes)

4. [Submit your work by pushing changes to Github](#submit-your-work)

# Initialize a New Project
1. On the main page for **this Github repository** click on the *Clone or download* button.
2. In the dialog box that posp up, click "Use SSH", then click on the clipboard icon to copy the repo URL.
3. In RStudio use the New Project command (from the Project menu)
4. Choose "Version Control" in the *Create Project* dialog box
5. Choose Git
6. Paste the repo URL into the *Repository URL*.  It should be something like `git@github.com:IBIEM/challenge_1.git`, but with your Github username as part of it.
7. For *Project directory name* put `challenge_1`
8. Leave *Create project as subdirectory of* as "~"
9. Click Create Project.

# Modifiying an Existing R Notebook
## Modify Rmarkdown
1. Author
2. Change color

# New R Notebook
1. Use the *File* menu to to open a new R Notebook
2. Edit the YAML header (the stuff between the two sets of three dashes: `---`)
  1. Change the title to "Challenge 1, Part 2"
  2. Below the title add: `author: "YOUR NAME"`
3. Delete everything below the YAML header (below the second `---` separator)
4. Leave a blank line below the YAML header, then add a section header: `# Comparing City and Highway Fuel Efficiency`
5. Below the section header, add the following chunk of R code:
```{r}
library(ggplot2)

ggplot(mpg, aes(cty, hwy, color = class)) + 
  geom_point()
```
6. Save the file as `challenge1_part2` (RStudio will automatically add ".Rmd") 
7. Knit the R Notebook to HTML by clicking on the triangle next to the *Knit* button (it might say *Preview* instead of *Knit*) and selecting *Knit to HTML*
8. If the knitting is successful, RStudio should pop open another window with the results.  It should look something like [this](challenge1_part2.html).
9. Follow the directions below for [Committing Changes](#commit-changes).  For this part of the assignment you should commit:
  - challenge1_part2.Rmd: the R Notebook that you created
  - challenge1_part2.html: the HTML file you knitted from your R Notebook

# Knit the Rmarkdown

# Commit Changes

# Submit Your Work
